---
title: "SDS 315 HW 9"
subtitle: ""
author: "Sophia Yang (sy23928)"
output:
  pdf_document:
    toc: true
    toc_depth: 5
    number_sections: false
date: "2025-04-16"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(ggplot2)
library(tidyverse)
library(mosaic)
library(moderndive)
library(effectsize)
```

# Problem 1
```{r, include = FALSE}
solder <- read.csv("solder.csv")
```

## Part A.
```{r}
# plot providing evidence that the opening is related to skips
ggplot(solder) + geom_boxplot(aes(x = Opening, y = skips)) +
  labs(
    title = "Relationship Between Opening Size and Skips",
    x = "Opening Size",
    y = "Number of Skips"
  )
```
The above boxplot displays the relationship between the size of the opening on a circuit board's solder gun (large, medium, or small) and the number of solder skips on the circuit board. Visually, circuit boards with larger openings have a lower number of skips than boards with smaller openings.

```{r}
# plot providing evidence that solder is related to skips
ggplot(solder) + geom_boxplot(aes(x = Solder, y = skips)) +
  labs(
    title = "Relationship Between Alloy Thickness and Skips",
    x = "Alloy Thickness",
    y = "Number of Skips"
  )
```
The above boxplot displays the relationship between the thickness of the alloy used for soldering (thick or thin) and the number of solder skips on the circuit board. Visually, circuit boards with thick alloy have a lower median number of skips than boards with thin alloy.

\newpage
## Part B.
```{r, include = FALSE}
# build a regression model, find 95% confints
skips_lm <- lm(skips ~ Opening + Solder + Opening:Solder, data = solder)
get_regression_table(skips_lm, conf.level = 0.95, digits = 2)
```

|                          | Estimate | 95% Confidence Interval |
|--------------------------|----------|-------------------------|
| **Intercept**            | 0.39     | (-0.63, 1.41)            |
| **OpeningM**             | 2.41     | (0.96, 3.85)            |
| **OpeningS**             | 5.13     | (3.68, 6.57)            |
| **SolderThin**           | 2.28     | (0.84, 3.72)            |
| **OpeningM\*SolderThin** | -0.74    | (-2.78, 1.30)           |
| **OpeningS\*SolderThin** | 9.65     | (7.61, 11.70)           |


## Part C.
The baseline number of skips for circuit boards that have large opening sizes and thick soldering alloy is 0.39 skips.
The main effect for the OpeningM variable is 2.41 skips. This is the effect of OpeningM in isolation.
The main effect for the OpeningS variable is 5.13 skips. This is the effect of OpeningS in isolation.
The main effect for the SolderThin variable is 2.28 skips. This is the effect of SolderThin in isolation.
The interaction effect for OpeningM and SolderThin is -0.74 skips. In other words, circuit boards that have both medium opening sizes and thin soldering alloy yield average skips that are 0.74 skips less than what you would expect from summing the individual “isolated” effects of the two variables (so 2.41 + 2.28 - 0.74).
The interaction effect for OpeningS and SolderThin is 9.65 skips. In other words, circuit boards that have both small opening sizes and thin soldering alloy yield average skips that are 9.65 skips more than what you would expect from summing the individual “isolated” effects of the two variables (so 2.28 + 5.13 + 9.65).


## Part D.
I would recommend a combination of large opening sizes and thick soldering alloy, because this combination produces the minimum number of skips: 0.39. 


\newpage
# Problem 2
```{r, include = FALSE}
grocs <- read.csv("groceries.csv")
```

## Part A.
```{r}
# find the avg price of products for each store
grocs_mean <- grocs |>
  group_by(Store) |>
  summarize(avg_price = mean(Price)) 

# graph store over avg price of products
ggplot(grocs_mean) + geom_col(aes(x = avg_price, y = Store)) +
  labs(
    title = "Relationship Between Store and Average Price",
    x = "Average Price"
  )
```
The above bar graph displays the relationship between the store and the average price of products sold. It appears that Whole Foods has the highest average price of products, while Fiesta has the lowest.


## Part B.
```{r}
# find the number of stores selling each product
grocs_stores <- grocs |> 
  group_by(Product) |>
  summarize(count = n())

# graph product over number of stores selling that product
ggplot(grocs_stores) + geom_col(aes(x = count, y = Product)) +
  labs(
    title = "Relationship Between Product and Number of Stores",
    x = "Number of Stores"
  )
```
The above bar graph displays the relationship between the product and the number of stores selling that product. It appears that Horizon 2% milk cartons and cartons of eggs are sold at the highest number of stores, while Lucky Charms (1 lb), Frosted Flakes (1 lb), El Milagros Tortilla Chips, and Cinnamon Toast Crunch (1 lb) are sold at the lowest number of stores.

\newpage
## Part C.
```{r, include = FALSE}
# build a regression model, find the 95% confints
groc_type_lm <- lm(Price ~ Product + Type, data = grocs)
get_regression_table(groc_type_lm, conf.level = 0.95, digits = 2)
```
Compared with ordinary grocery stores, convenience stores charge somewhere between 0.41 and 0.92 dollars more for the same product.


## Part D.
```{r, include = FALSE}
# build a regression model
groc_store_lm <- lm(Price ~ Product + Store, data = grocs)
get_regression_table(groc_store_lm, conf.level = 0.95, digits = 2)
```
Walmart and Kroger Fresh Fare seem to charge the lowest prices when comparing the same product, while Whole Foods and Wheatsville Food Co-Op seem to charge the highest prices when comparing the same product.


## Part E.
The possibility that Central Market charges a similar amount to HEB for the same product looks right to me: the coefficient for the Central Market is -0.57 with a 95% confidence interval of (-0.92, -0.23), while the coefficient for HEB is -0.65 with a 95% confidence interval of (-0.95, -0.35). Because the difference between the coefficient estimates is only 0.08, and because their confidence intervals overlap, it looks more possible to me that Central Market charges a similar amount to HEB for the same product. Compared to differences among other stores, the difference between HEB and Central Market is small. For example, the difference between Walmart, which has a coefficient of -0.99, and Whole Foods, which has a coefficient of 0.36, is 1.35, which is much larger than 0.08.


## Part F.
```{r, include = FALSE}
# create an Income10K var
groc_income <- grocs |>
  mutate(Income10K = Income/10000)

# build a regression model
groc_income_lm <- lm(Price ~ Product + Income10K, data = groc_income)
coef(groc_income_lm)

# standardize coefficients
standardize_parameters(groc_income_lm)
```
Based on the fact that the Income10K coefficient is negative, consumers in poorer ZIP codes seem to pay more for the same product, on average, because for every 10,000 dollar increase in income, the price decreases by 0.01 dollars. 
A one-standard deviation increase in the income of a ZIP code seems to be associated with
a -0.03 standard-deviation change in the price that consumers in that ZIP code expect to pay for
the same product.

\newpage
# Problem 3

## Statement A.
True, because Figure A1 shows a positive correlation between the percentage of minority residents in a ZIP code and FAIR policies per 100 housing units. Additionally, the 95% confidence interval for the slope between these two variables is (0.009, 0.018), which does not include 0. Thus, we can conclude that ZIP codes with a higher percentage of minority residents tend to have more FAIR policies per 100 housing units.

## Statement B.
Undecidable, because although Figure B1 shows a positive slope estimate between minority percentage and the age of the housing stock, the 95% confidence interval for this slope is (-0.116, 0.912), which includes 0. Thus, we cannot for sure say that there is an interaction effect between minority percentage and the age of the housing stock. In order to decide the question, I'd like to see more evidence on the correlation between minority percentage and the age of the housing stock.

## Statement C.
Undecidable, because although Figure C1 shows that the group with a high-fire-risk has a steeper slope estimate (stronger relationship) between the minority percentage and the number of FAIR policiers per 100 housing units than the group with a low-fire-risk, the 95% confidence intervals for the coefficients of low-fire-risk and the interaction variable is (-0.995, 0.109) and (-0.012, 0.01), respectively, which both include 0. Thus, we cannot for sure say that the relationship between minority percentage and number of FAIR policies per 100 housing units is stronger in high-fire-risk ZIP codes than in low-fire-risk ZIP codes. In order to decide the question, I'd like to see more evidence on the coefficient estimates for the low-fire-risk and interaction variables.

## Statement D.
False. I'd correct that income "explains away" part of the association between minority percentage and FAIR policy uptake, because although Model D shows that income has a stronger effect on the number of FAIR policies than minority does, if income explained away all the association, then the coefficient for minority would be 0 after adding the income variable. However, Model D1 shows that the coefficient for minority is still relatively the same as before (around 0.01).

## Statement E.
True, because Model E shows that even after adding in the income, fire risk, and housing age variables, there is still a positive slope estimate between minority percentage and number of FAIR policies. Additionally, the 95% confidence interval for that slope is (0.003, 0.014), which does not include 0. Thus, we can conclude that minority percentage and number of FAIR policies are still associated at the ZIP code level, even after controlling for income, fire risk, and housing age.